---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# nhlmodelr: Spatial Modelling of NHL Shot Location Data



Access pre-formatted NHL shot location data and implement spatially explicit models of NHL goal scoring probability. Advanced team, player, and goaltender statistics can be automatically calculated.

## Installation

```{r gh-installation, eval = TRUE, message = FALSE, warning = FALSE}
devtools::install_github("jedalong/nhlmodelr")
```
  
## Quick demo

Load  in some data (2011-12 season) and take a look at the structure.

```{r}
library(nhlmodelr)
data(shots20112012) 
head(shots20112012)
summary(shots20112012)
```

Next, format the shots for the spatial model by spatially pooling all the shots to the 5525 unique locations in the offensive zone.

```{r}
modshots <- shots2model(shots20112012)
head(modshots)
```

Set up parameters for the spatial model. First, we need to set the number of Gibbs samples for the MCMC chain and the burn-in. We also need to set-up initial values for each location (here we use random values between 0 and 1). The parameter p.max is the tuning parameter, which is the maximum probability of scoring a goal (in the centre of the goal). Finally, the output filename for storing output \*.RData file needs to be specified (the model produces a single \*.RData file with 8 objects, see  ?NHLmodelr).

```{r}
ngibbs <- 100
nburnin <- 50
p.max <- 0.29
inits <- runif(dim(modshots)[1],0,1)
outfile <- 'C:/Workspace/NHLModelOutput.RData'

#Model Run - Takes a couple of minutes
df <- NHLmodel(modshots,ngibbs,nburnin,p.max,inits,outfile)
head(df)
```

Their are a number of plotting functions available. We can plot the raw shots data, only the goals, the posterior mean, and the posterior variance. Note: The posterior mean and variance here are unrealistic as they are based on only 100 Gibbs samples from the MCMC run.

```{r}
NHLmodelplot(df,'shots')
NHLmodelplot(df,'goals')
NHLmodelplot(df,'postmean')
NHLmodelplot(df,'postvar')
```

We can also compute advanced team, player, and goaltender spatially adjusted scoring (and save percentage) statistics.

```{r}
#==== Not Run ====
# teamdb <- teams(df,shots20112012)
# playerdb <- players(df,shots20112012)
# goaliedb <- goalies(df,shots20112012)
#====
```

--- End ---
